---
title: "Assignment 1 Econ 220"
author: "D.Z."
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Download data into R
Here is the code to download your data from excel

```{r}
library(readxl)
data18 <- (read_excel("YourData_F2018.xlsx", range = "B7:F73"))
```

## Descriptive statistics of the data

First make a summary of the data
```{r}
summary(data18)
```

Now let's look at statistics by gender
```{r}
data18 %>%
  group_by(Gender) %>%
  summarise(Height = mean(Height), Weight = mean(Weight), Shoe_size = mean(Shoe_size), Pair_Shoes = mean(Pair_Shoes))
```

What is the correlation between height and weight by gender
```{r}
data18 %>%
  group_by(Gender) %>%
  summarise(round(cor(Height, Weight), 2))
```


## Graphs

Make the following graphs * One that show the relationship between height and weight by gender * Average shoe size by gender * Average show pair of shoes by gender

```{r}
data18 %>%
  group_by(Gender) %>%
  ggplot(aes(x = Weight, y = Height)) +
  geom_point(aes(color = Gender), alpha = 0.5) +
  facet_grid(. ~Gender)
```

```{r}
data18 %>%
  group_by(Gender) %>%
  summarise(average_size = round(mean(Shoe_size), 0)) %>%
  ggplot(mapping = aes(x = Gender, y = average_size, label = average_size)) +
  geom_col(fill = "light green") +
  geom_text(size = 8, fontface = 1, color = "red", position = position_stack(vjust = 0.5)) +
  ylab("Shoe_Size") + xlab("Gender") + 
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
data18 %>%
  group_by(Gender) %>%
  summarise(average_pair = round(mean(Pair_Shoes), 0)) %>%
  ggplot(mapping = aes(x = Gender, y = average_pair, label = average_pair)) +
  geom_col(fill = "dark blue") +
  geom_text(size = 8, fontface = 1, color = "yellow", position = position_stack(vjust = 0.5)) +
  ylab("Pair_of_Shoes") + xlab("Gender") +
  ggtitle("Average Pair of Shoes by Gender") +
  theme(plot.title = element_text(hjust = 0.5))
```

