---
title: "Tables_Assignment"
author: "D.Z."
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    theme: united
---

```{css, echo=F}
th, td {
    padding-left: 10px;
    text-align: left;        
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(stargazer)
```

# In class assignment 

Use this empty R markdown document to practice your skills to do nice tables in R. 

1. Load the R built in dataset `swiss` that contains a standardized fertility measure and socio-economic indicators for each of 47 French-speaking provinces of Switzerland at about 1888.
**Hint**: Remember to add the option results='asis' in every chunk of code that uses stargazer to make sure your results print nicely onto html.

2. Create the basic summary table
```{r}
summary(swiss)
```


3. Use kable to make a nicer looking table 
```{r}
kable(summary(swiss), digits=2, caption="Swiss Data")
```


4. Use `stargazer` to make a `drop dead gorgeous` table with the summary statistics. Only showing only n, mean, and sd.
```{r, results='asis'}
stargazer(swiss, type = "html", digits = 1, summary.stat = c("n", "mean", "sd")) 
```


5. Make the same table as before but flip it and change the title.
```{r, results= 'asis'}
stargazer(swiss, type = "html", summary.stat = c("n", "mean", "sd"), flip = TRUE, title= "My beautiful table",
          out = "Nice_table.html")
```


 